Peripheral Edema measurement methods (by ArticleAggregator_v03)

### 2022-11-02 ArticleAggregator_v05_pure.qmd
1st time FUNCTIONAL :)

write_xlsx(eb, glue("{aa_path}eb_to_merge.xlsx"))
# Correct for Van Der Lee manually

@@

# art_title <- gs %>% html_elements("h3 a") %>% html_text()
# art_info <- gs %>% html_elements(".gs_a") %>% html_text()
# art_ref <- gs %>% html_elements(".gs_rt") %>% html_elements("a") %>% html_attr("href")
# output_df <- data.frame(title=art_title, info=art_info, ref=art_ref)
# write_xlsx(res_df, glue("{aa_path}gs_raw.xlsx"))
```

@@

```{r}
#| label: Expand Google Search (gs) columns to fit with EMBASE
gs <- sep_df %>% 
  mutate(PubDate = NA) %>% 
  mutate(PubType = NA) %>%
  mutate(Abstract = NA) %>% 
  mutate(CT = NA) %>%
  mutate(PMID = NA) %>% 
  mutate(PUI = NA) %>%
  mutate(DOI = NA) %>% 
  mutate(EBlink = NA) %>%
  mutate(OpenLink = NA) %>% 
  mutate(Src = "GoogleScholar") %>% 
  select(Title, Author, Year, FTlink, Src, Info, everything())

write_xlsx(gs, glue("{aa_path}gs_to_merge.xlsx"))
## Manually input missing values ;)
```
## Pubmed

You can get full-text link using Elink method of NIH e-utilities tool

```{r}
#| label: PubMed connection
api_key <- "0b1204719f054732c66e608d9d3f2c749c08"
pm_query <- glue('peripheral edema measurement')
my_entrez_id <- get_pubmed_ids(pm_query, api_key=api_key)
# my_abstracts_txt <- fetch_pubmed_data(my_entrez_id, format = "abstract")
# print(my_abstracts_txt[1:45])

my_abstracts_xml <- fetch_pubmed_data(pubmed_id_list = my_entrez_id)
print(paste0("Query retireved ",my_entrez_id$Count," records."))
# print(my_abstracts_xml)
# write(my_abstracts_xml, file = "PubMed_records_by_write.xml")
# recs <- read_xml(my_abstracts_xml) #  From DB connection
recs <- read_xml(paste0(aa_path, "PubMed_records_by_write.xml")) # From file

# USE THIS  TO EXTRACT ALL FIELDS AND CHARACTER VECTOR AND JOIN TO DATAFRAME

xml_abstract_n <- recs %>% xml_find_all(".//Abstract") %>% length()
xml_pmid_n <- recs %>% xml_find_all(".//MedlineCitation/PMID | .//BookDocument/PMID") %>% length()
xml_year_n <- recs %>% xml_find_all(".//PubDate/Year | .//PubDate/MedlineDate") %>% length()
xml_author_n <- recs %>% xml_find_all(".//AuthorList") %>% xml_find_first(".//Author/LastName") %>% length()
xml_title_n <- recs %>% xml_find_all(".//ArticleTitle") %>% length()

# CONTINUE HERE ----
# Some articles have Either EIdType OR IdType OR BOTH.I need IF to remove those with both
xml_doi_n <- recs %>% xml_find_all(".//Article/ELocationID[@EIdType='doi']") %>% length() # N201
xml_doi_n <- recs %>% xml_find_all(".//PubmedData/ArticleIdList/ArticleId[@IdType='doi'] | .//Article/ELocationID[@EIdType='doi']") %>% length() # N528
# WRONG if
# inspire here: https://stackoverflow.com/questions/30604107/r-conditional-evaluation-when-using-the-pipe-operator
xml_doi_n <- recs %>% {if(xml_find_all(".//PubmedData/ArticleIdList/ArticleId[@IdType='doi']") . else xml_find_all(".//Article/ELocationID[@EIdType='doi']")} %>% length()

art <- ".//PubmedArticle | .//PubmedBookArticle"
e_doi <- ".//Article/ELocationID[@EIdType='doi']"
p_doi <- ".//PubmedData/ArticleIdList/ArticleId[@IdType='doi']"
n_art <- recs %>% xml_find_all(art)
xml_doi_n <- recs %>% xml_find_all(art) %>%
  map(if(is_empty(xml_find_first(p_doi)))
  xml_find_first(e_doi) else
  xml_find_first(p_doi)) %>% 
  length()

xml_doi_n <- recs %>% xml_find_all(art) %>%
  map(., ~ifelse(is_empty(xml_find_first(.x, p_doi)), 
  xml_find_first(e_doi),
  xml_find_first(p_doi))) %>% 
  length()

{if(is_empty(xml_find_all(".//PubmedData/ArticleIdList/ArticleId[@IdType='doi']"))
                          . else xml_find_all(".//Article/ELocationID[@EIdType='doi']")} %>% length()
# LOOP: take each article. IF "have both" take "IdType" only. Do for each node and append doi to resulting vector. Use for loop.

# Count of doi should be 372 BUT is 327 :) Correction needed.
xml_pubtype_n <- recs %>% xml_find_all(".//PublicationTypeList | .//BookDocument") %>% xml_find_first(".//PublicationType") %>% length()
xml_nodes_count <- data.frame(xml_abstract_n, xml_pmid_n, xml_year_n, xml_author_n, xml_title_n, xml_doi_n, xml_pubtype_n)
print(xml_nodes_count)
rm(list = ls(pattern='_n$'))

### Split xml by items to data.frame rows ----
library(dplyr)
library(xml2)
library(purrr)
library(tidyr)
xml <- xml2::read_xml("input/example.xml")
rows <- xml %>% xml_find_all("//xmlsubsubnode")
rows_df <- data_frame(node = rows) %>%
  mutate(node_id = node %>% map(~ xml_find_first(., "ancestor::xmlnode")) %>% map(~ xml_attr(., "node-id"))) %>%
  mutate(subnode_id = node %>% map(~ xml_parent(.)) %>% map(~ xml_attr(., "subnode-id"))) %>%
  mutate(text = node %>% map(~ xml_text(.))) %>%
  select(-node)
# https://stackoverflow.com/questions/49253021/how-to-extract-xml-attr-and-xml-text-on-different-levels-with-xml2-and-purrr

xml_articles <- recs %>% xml_find_all(".//PublicationTypeList | .//BookDocument")
xml_articles[[1]][["doc"]]
df_articles <- tibble(item = xml_articles)
ls_articles <- as.list(xml_articles)

### 5 Cases for DOI ----
xml_5_doi <- recs %>%
  xml_find_all(".//Article[@PubModel='Print']/../../PubmedData/ArticleIdList/ArticleID[@IdType='doi']") %>%
  length()

### THIS WORKS ----
xml_5_doi_tested <- recs %>%
  xml_find_all("//Article[@PubModel='Print']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi']") %>%
  xml_text()

xml_5_doi <- recs %>%
  xml_find_all("//Article[@PubModel='Print']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi'] |
                //Article[@PubModel='Print-Electronic']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi'] |
                //Article[@PubModel='Electronic']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi'] |
                //Article[@PubModel='Electronic-eCollection']/ancestor::PubmedArticle//ELocationID[@EIdType='doi']
               ") %>%
  length()

### CODE below generates 327 instead of 371 Captures ----
xml_5_doi <- recs %>%
  xml_find_all("//Article[@PubModel='Print']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi'] |
  //Article[@PubModel='Print-Electronic']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi'] |
  //Article[@PubModel='Electronic']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi'] |
  //Article[@PubModel='Electronic-eCollection']/ancestor::PubmedArticle//ELocationID[@EIdType='doi']
  ") %>%
  length()

# Analysis of problematic PubModel ----
recs %>% xml_find_all("//Article[@PubModel]='Electronic'") %>% length() # Correct, 371 because one is PubmedBookArticle

recs %>% xml_find_all("//PubmedArticle") %>% length() # Correct, 371 because one is PubmedBookArticle

recs %>% xml_find_all("//Article[@PubModel='Print']") %>% length() # 207
recs %>% xml_find_all("//Article[@PubModel='Print']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi']") %>% length() #165

recs %>% xml_find_all("//Article[@PubModel='Print-Electronic']") %>% length() # 138
recs %>% xml_find_all("//Article[@PubModel='Print-Electronic']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi']") %>% length() # 137

recs %>% xml_find_all("//Article[@PubModel='Electronic']") %>% length() # 21
recs %>% xml_find_all("//Article[@PubModel='Electronic']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi']") %>% length() # 20

recs %>% xml_find_all("//Article[@PubModel='Electronic-eCollection']") %>% length() # 5
recs %>% xml_find_all("//Article[@PubModel='Electronic-eCollection']/ancestor::PubmedArticle/PubmedData/ArticleIdList/ArticleId[@IdType='doi']") %>% length() #5

PubmedArticle_n <- recs %>% xml_find_all("/PubmedArticleSet/PubmedArticle") %>% length() # Is correctly 371; PubmedArticle[369] missing; does not have ANY DOI
PubmedArticle_369 <- recs %>% xml_find_all("/PubmedArticleSet/PubmedArticle[369]//ArticleTitle") %>% xml_text()

models <- recs %>% xml_find_all("//Article[@PubModel]") %>% xml_attr("PubModel") %>% as.factor() %>% levels()
models

# Find which nodes are missing in 327 nodes. ----
node_path_n <- recs %>% xml_find_all("//*[@*='doi']") %>% length()
node_path <- recs %>% xml_find_all("//*[@*='doi']") %>% xml_path()
node_path
node_mode <- recs %>% xml_find_all("//*[@*='doi']/ancestor::Article[@PubModel]") %>% length()
write.csv(node_path, glue("{aa_path}node_path.csv"))

# xml_5_doi <- recs %>% 
#   xml_find_all(".//Article[@PubModel='Print']/ancestor::PubmedArticle") %>% xml_text()
#   xml_find_all(".//ArticleID[@IdType='doi']")
#   length()

xml_abstract <- recs %>% xml_find_all(".//Abstract") %>% xml_text()
xml_pmid <- recs %>% xml_find_all(".//MedlineCitation/PMID | .//BookDocument/PMID") %>% xml_text()
xml_year <- recs %>% xml_find_all(".//PubDate/Year | .//PubDate/MedlineDate") %>% xml_text()
xml_author <- recs %>% xml_find_all(".//AuthorList") %>% xml_find_first(".//Author/LastName") %>% xml_text()
xml_title <- recs %>% xml_find_all(".//ArticleTitle") %>% xml_text()
xml_doi <- recs %>% xml_find_all(".//PubmedData/ArticleIdList/ArticleId[@IdType='doi']") %>% xml_text()
xml_pubtype <- recs %>% xml_find_all(".//PublicationTypeList | .//BookDocument") %>% xml_find_first(".//PublicationType") %>% xml_text()

pm_src <- data.frame(xml_title, 
                 xml_author,
                 xml_year,
                 xml_doi,
                 xml_pmid,
                 xml_abstract,
                 xml_pubtype)

pm <- pm_src %>% 
  mutate(FTlink = paste0("https://dx.doi.org/",pm_src$xml_doi)) %>% 
  mutate(CT = NA) %>% 
  mutate(PUI = NA) %>%
  mutate(PubDate = NA) %>%
  mutate(EBlink = NA) %>%
  mutate(OpenLink = NA) %>% 
  mutate(Info = NA) %>% 
  mutate(Src = "PubMed") %>% 
  select(xml_title, 
         xml_author, 
         xml_year, 
         FTlink, 
         Src, 
         Info, 
         PubDate, 
         xml_pubtype, 
         xml_abstract, 
         CT, 
         xml_pmid, 
         PUI, 
         xml_doi,
         EBlink,
         OpenLink)

names(pm) <- final_col_names
write_xlsx(pm, glue("{aa_path}pm_to_merge.xlsx"))
# rm(list = ls(pattern='^xml_'))
# rm(list=ls()[!ls() %in% c("eg")])

```
```{r}
#| label: Interating over PubMed (pm) article nodes
api_key <- "0b1204719f054732c66e608d9d3f2c749c08"
pm_query <- glue('peripheral edema measurement')
my_entrez_id <- get_pubmed_ids(pm_query, api_key=api_key)
# my_abstracts_txt <- fetch_pubmed_data(my_entrez_id, format = "abstract")
# print(my_abstracts_txt[1:45])
my_abstracts_xml <- fetch_pubmed_data(pubmed_id_list = my_entrez_id)
print(paste0("Query retireved ",my_entrez_id$Count," records."))
# print(my_abstracts_xml)
# write(my_abstracts_xml, file = "PubMed_records_by_write.xml")
recs <- read_xml(my_abstracts_xml)

xml_arts <- recs %>% xml_find_all(".//PublicationTypeList | .//BookDocument")
##  CONTINUE HERE ----
art_title <- xml_arts %>% map_dfc(pm_ex(.))
pm_ex <- function(x){ 
  art_title <- x %>% xml_find_first(".//ArticleTitle") %>% xml_text()
  return(art_title)
}
art_title <- xml_arts[[1]] %>% xml_find_first(".//ArticleTitle") %>% xml_text()
print(xml_arts[1])

```
```{r}
#| label: Split items children to tibble / data_frame
xml_in_df <- recs %>% xml_find_all(".//PubmedArticle | .//PubmedBookArticle" ) %>% 
  map(xml_children) %>% 
  map(~as_tibble(t(set_names(xml_text(.), xml_name(.))))) #or map_df
```

```{r}
#| label: Split items to tibble / data_frame
xml_in_df <- recs %>% xml_find_all(".//PubmedArticle | .//PubmedBookArticle" ) %>% 
  map(xml_contents) %>% 
  map(~as_tibble(t(set_names(xml_text(.), xml_name(.))))) #or map_df
```

```{r}
#| label: Merge results from embase (eb), Google Scholar (gs), and PubMed (pm)
eb <- read_xlsx(glue("{aa_path}eb_to_merge.xlsx"))
gs <- read_xlsx(glue("{aa_path}gs_to_merge.xlsx"))
pm <- read_xlsx(glue("{aa_path}pm_to_merge.xlsx"))

egp <- bind_rows(eb, gs, pm) %>% 
  arrange(desc(Year), Author, Src)
# rm(list=ls()[!ls() %in% c("eg")])
# write_xlsx(egp, glue("{aa_path}egp_v02.xlsx"))
```
# ToDo
- correct PubMed functionality
- gs extract surnames that include hyphen
- Introduce SrchIndex
- Add columns: Status, Priority

>>>>

# write_xlsx(eb, glue("{aa_path}eb_to_merge.xlsx"))
# Correct for Van Der Lee manually

@@

# art_title <- gs %>% html_elements("h3 a") %>% html_text()
# art_info <- gs %>% html_elements(".gs_a") %>% html_text()
# art_ref <- gs %>% html_elements(".gs_rt") %>% html_elements("a") %>% html_attr("href")
# output_df <- data.frame(title=art_title, info=art_info, ref=art_ref)
# write_xlsx(res_df, glue("{aa_path}gs_src.xlsx"))
```

@@

```{r}
#| label: Expand Google Search (gs) columns to fit with EMBASE
gs <- sep_df %>% 
  mutate(PubDate = NA) %>% 
  mutate(PubType = NA) %>%
  mutate(Abstract = NA) %>% 
  mutate(CT = NA) %>%
  mutate(PMID = NA) %>% 
  mutate(PUI = NA) %>%
  mutate(DOI = NA) %>% 
  mutate(EBlink = NA) %>%
  mutate(OpenLink = NA) %>% 
  mutate(Src = "GoogleScholar") %>% 
  mutate(SrcIndex=row_number()) %>%
  select(Title, Author, Year, FTlink, Src, Info, everything())

# write_xlsx(gs, glue("{aa_path}gs_to_merge.xlsx"))

## Manually input missing values ;)
```
## Pubmed
```{r}
#| label: PubMed connection and article extraction
api_key <- "0b1204719f054732c66e608d9d3f2c749c08"
pm_query <- "peripheral[tiab] edema[tiab] measurement[tiab]"
# pm_query <- glue("{term}[tiab]")
my_entrez_id <- get_pubmed_ids(pm_query, api_key=api_key)
my_entrez_id$QueryTranslation
my_entrez_id$Count

# Get articles XML
my_abstracts_xml <- fetch_pubmed_data(pubmed_id_list = my_entrez_id, 
                                      retmax=500, 
                                      format="xml", 
                                      encoding="UTF-8")
# print(paste0("Query retireved ",my_entrez_id$Count," records."))
# print(my_abstracts_xml)
write(my_abstracts_xml, file = "PubMed_records_by_write.xml")

ls_recs <- articles_to_list("PubMed_records_by_write.xml")
# ls_recs <- my_abstracts_xml

# Extract info form the list of articles
pm_df <- ls_recs %>% 
  map_df(~ article_to_df(.x, autofill = TRUE, getAuthors = TRUE, getKeywords = TRUE)) %>% 
  distinct(pmid, .keep_all=TRUE) %>%
  select(title, lastname, year, abstract, pmid, doi)

# Add columns
names(pm_df) <- c("Title", "Author", "Year", "Abstract", "PMID", "DOI")
pm <- pm_df %>% 
  mutate(Info = NA) %>% 
  mutate(PubDate = NA) %>% 
  mutate(PubType = NA) %>%
  mutate(CT = NA) %>%
  mutate(PUI = NA) %>%
  mutate(EBlink = NA) %>%
  mutate(OpenLink = NA) %>%
  mutate(FTlink = paste0("https://dx.doi.org/",pm_df$DOI)) %>% 
  mutate(Src = "PubMed") %>% 
  mutate(SrcIndex=row_number()) %>%
  select(Title, Author, Year, FTlink, Src, Info, everything())
write_xlsx(pm, glue("{aa_path}pm_to_merge.xlsx"))

```
## Merge the results
```{r}
#| label: Merge results from embase (eb), Google Scholar (gs), and PubMed (pm)
eb <- read_xlsx(glue("{aa_path}eb_to_merge.xlsx"))
gs <- read_xlsx(glue("{aa_path}gs_to_merge.xlsx"))
pm <- read_xlsx(glue("{aa_path}pm_to_merge.xlsx"))

egp <- bind_rows(eb, gs, pm) %>%
  mutate(Status=NA) %>% 
  mutate(Priority=NA) %>% 
  arrange(desc(Year), Author, Src) %>% 
  select(Status, Priority, everything())
# rm(list=ls()[!ls() %in% c("eg")])
write_xlsx(egp, glue("{aa_path}egp_v01.xlsx"))
```

# ToDo
- gs extract surnames that include hyphen
- Add columns: Status, Priority
